% Josh Cronemeyer's Resume: Version 0.5.1
%
% Should resume versions have meaning besides the standard ordinal significance?
% Leave a comment here: http://www.cuberick.com/2009/05/building-your-resume.html
% If you have any ideas about this.  Here are mine:
% Decade.Year.Resume (so mine is the first resume version from my 5th professional year)
% Year.Project.Resume (My first year. Fifth professional project. First resume of that year)

% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{JOSH CRONEMEYER\\[12pt]}     % the \\[12pt] adds a blank
                % line after name
                      
%FILL_IN_TOP_SECRET_ADDRESS
                                  
\begin{resume}

\section{EDUCATION}          
    University Of Kansas,  \\        
    Bachelor of Science, Computer Science, May 2002   \\       
    Bachelor of Arts, Italian, May 2002  %WOOT Italian degree!  I can
    %still speak fluently and I'd love to go back to Italy.  Please,
    %please, please drop me a line if you want to pay me to work in
    %Italy. 
 
\section{EXPERIENCE}
   \vspace{-0.1in}  
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Senior Consultant} \>ThoughtWorks     \>Feb. 2006-Present

   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    I Worked as a programmer on a 20+ developer Agile project for
    a well known e-commerce site.  The application had complex
    integration requirements, high traffic and performance needs,
    and as usual the deadline was ultra tight. Technologies included 
    Spring MVC and Mule ESB. %Nondisclosure agreements make it necessary
    %for me to put stuff like "well known company x" :( Even in comments.
    
    I Worked as a developer on a frontend equipment leasing application 
    for a well known manufacturer.  The project was a 10+ year old
    EJB application running on Weblogic.  With nearly 6000 class files
    it would even make someone who wrote the book on legacy code 
    (Michael Feathers) get sweaty armpits.  Add to that equation the 
    fact that the domain of leasing is particularly challenging and 
    you get the picture.  This project was a bear. %Martin fowler
    %talks about this project.  And hey!  He speaks fondly of it
    %http://martinfowler.com/bliki/NashvilleProject.html
    %I too get all choked up just thinking of our 25 minute
    %cruise build and the session beans.

    As part of a smaller Agile team for Inveneo (a nonprofit startup TW
    did pro bono work for) I was tech lead in charge of delivering 
    a build and test system for Ubuntu installer ISOs. This is the
    best project I've ever been on since the software was for bringing 
    technology to remote places in Africa.
    %powered by impereal rolls from tu-lan and coffee from the
    %blue bottle.  http://www.yelp.com/biz/tu-lan-san-francisco

    Another small Agile team I worked on delivered a reporting tool
    at an investment bank in London.  This was a small piece of a 
    much larger programme that was subsequently cancelled due to 
    a very difficult political situation within the company.  Even
    with the premature end of the project we delivered working software
    to the client.  Thanks XP! %We almost got to use why the lucky
    %stiff's 'shoes' as the GUI technology!

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Programmer} \>NIC \> Mar. 04-Jan. 06\\
                          \>Topeka, KS
   \end{tabbing}\vspace{-20pt}
    Developed and maintained Java servlets for the State of Kansas
    including: kslegislature.org, the Kansas board of Technical 
    Professionals and the Kansas Board of Emergency Medical Services.
    %Awesome! Nearly 5 years have come and gone and all these old
    %struts apps I did are still kicking it!  Go, man go!

\section{OTHER}          
    I presented at OSCON (twice), Open Source Bridge, Chicago Ruby 
    User Group and the Chicago Python User Group.  I love Open 
    Source and have my own seldom used project called Shell-Sink.  
    I made minor contributions to Mocha, Debian-CD and implemented 
    migrations for Rails Fixtures.
    %Ok, so I implemented migrations for Rails database fixtures, 
    %but then I realized that fixtures were just a bad idea to
    %begin with so eventually my friends talked me down from 
    %trying to get that included in rails core.  Thank goodness.

\section{SKILLS AND PROGRAMMING LANGUAGES}          
    Java, Ruby, Python, Bash, Scala, Linux, XP/Agile, General 
    consulting, Being Honest, Having fun.
    %I can't stand it when people throw every technology they have
    %ever heard of onto their skills section.
    %Scala is a real stretch, since i'm just learning it, but hey
    %I'd like to write some scala for pay someday.
     
\section{JUST FOR FUN}          
    Avid home brewer, baker, biker, climber, and runner.
    %Seriously, this is one of the most important parts of a resume.
    %I'm waving my hands hoping the person reading it has a soul and
    %notices I have one too.

\end{resume}
\end{document}
